---
title: "Review Presentation for Will"
output:
  html_document: default
  html_notebook: default
---

A list of all the figures and tables to go into the biophysical connectivity review paper

```{r include=FALSE}
#load libraries
library("tidyverse")
##library("readxl")
#load data
##df <- read_excel("data/lit_review.xlsx",sheet=1,col_names=TRUE,na="NA")
data.all <- read_csv("data/lit_review.csv")
```

```{r include=FALSE}
#check the columns loaded
spec(data.all)
```

Summary of all the data
```{r}
#get a summary of all the data
summary(data.all)
```

##General summary section

###The years the studies were published

```{r}
data.all <- data.all %>% mutate(movement = 
  Circatidal_migration |
  Pynocline_migration |
  Halocline_migration |
  Ontogentic_vertical_migration |
  Vertical_swimming_ability |
  Horizontal_swimming_ability |
  Sinking_velocity  | 
  Diel_vertical_migration) %>% mutate(settlement = Sensory_extent > 0)

##data.all.comparisons <- data.all %>% gather(Behaviours, Implemented, Passive_movement,movement)

data.all.comparisons <- data.all %>% gather(Behaviours, Implemented,Passive_movement,movement,Orientation,settlement)
data.papers.published <- data.all.comparisons %>% select(Paper_ID,Published,Behaviours,Implemented) %>% distinct(Paper_ID,Published,Behaviours,Implemented)
data.papers.published <- filter(data.papers.published,Implemented == TRUE)
ggplot(data.papers.published, aes(Published)) + geom_bar(aes(fill = Behaviours)) +labs( x = "Publication year", y = "Number of papers")
```
###Published studies for each model

```{r}
source("sort_factor.R")
ggplot(data.all,aes(SortFactorBySize(DOI))) + geom_bar() + theme(axis.text.x=element_blank(),
                        axis.ticks.x=element_blank()) + xlab("Individual model runs per study")
```
###Different taxa

```{r}
data.taxa <- select(data.all,Species_type) 
ggplot(data=data.taxa,aes(SortFactorBySize(Species_type))) + geom_bar() + coord_flip() + ylab("Number of models using the taxa") + xlab("Taxa")
```

###Oceangraphic regions
```{r}
data.regions <- data.all %>% select(Paper_ID,Oceanic_region) %>% distinct(Paper_ID,Oceanic_region)
data.regions %>% group_by(Oceanic_region) %>% summarise (n = n()) %>% mutate(freq = n / sum(n))
ggplot(data.regions,aes(SortFactorBySize(Oceanic_region)),fill=gray) + geom_bar() + coord_flip() + xlab("Oceanographic region") + ylab("Number of papers per region")
```


###Biophysical models used
```{r}
data.models <- data.all %>% select(Paper_ID,Model_name) %>% distinct(Paper_ID,Model_name)
data.models %>% group_by(Model_name) %>% summarise (n = n()) %>% mutate(freq = n / sum(n))
```


##Physical models
This section compares outputs of the physical models
###Physical models used
```{r}
data.model.ocean <- data.all %>% select(Paper_ID,Physical_model) %>% distinct(Paper_ID,Physical_model)
data.model.ocean %>% group_by(Physical_model) %>% summarise (n = n()) %>% mutate(freq = n / sum(n))
```

###Timestep

```{r}
data.papers.timestep <- data.all %>% select(Paper_ID,Model_time_step) %>% distinct(Paper_ID,Model_time_step) %>% na.omit()
ggplot(data.papers.timestep,aes(Model_time_step)) + geom_density() + xlab("Time step (seconds)")
```

####Metrics influence
```{r}
data.timestamp.sr <- select(data.all,Model_time_step,Self_recruitment_mean) %>% na.omit()
ggplot(data.timestamp.sr,aes(Model_time_step,Self_recruitment_mean)) + geom_point()

data.timestamp.lr <- select(data.all,Model_time_step,Local_retention_mean) %>% na.omit()
ggplot(data.timestamp.lr,aes(Model_time_step,Local_retention_mean)) + geom_point()

data.timestamp.ss <- select(data.all,Model_time_step,Settlement_success_mean)
ggplot(na.omit(data.timestamp.ss),aes(Model_time_step,Settlement_success_mean)) + geom_point()

```


###Model resolution and submodels
```{r}
data.papers.resolution <- data.all %>% select(Paper_ID,Model_resolution_min,Model_spatial_shape) %>% distinct(Paper_ID,Model_resolution_min,Model_spatial_shape)
data.papers.resolution.grid <- filter(data.papers.resolution,Model_spatial_shape == "Grid")
ggplot(data.papers.resolution.grid,aes(Model_resolution_min)) + geom_density() + xlab("The minimumn model resolution (seconds)")
```


####Self-recruitment
```{r}
data.resolution.sr <- data.all %>% filter(Model_spatial_shape == "Grid") %>%select(Model_resolution_min,Model_spatial_shape,Self_recruitment_mean,Nested_submodels) %>% na.omit() 
ggplot(data.resolution.sr,aes(Model_resolution_min,Self_recruitment_mean)) + geom_point()
ggplot(data.resolution.sr,aes(Nested_submodels,Self_recruitment_mean)) + geom_boxplot()+ geom_jitter(width = 0.2)
```
####Local retention
```{r}
data.resolution.lr <- data.all %>% filter(Model_spatial_shape == "Grid") %>%select(Model_resolution_min,Nested_submodels,Local_retention_mean) %>% na.omit()
ggplot(data.resolution.lr,aes(Model_resolution_min,Local_retention_mean)) + geom_point()
ggplot(data.resolution.lr,aes(Nested_submodels,Local_retention_mean)) + geom_boxplot()+ geom_jitter(width = 0.2)
```
####Settlement success
```{r}
data.resolution.ss <- data.all %>% filter(Model_spatial_shape == "Grid") %>%select(Model_resolution_min,Nested_submodels,Settlement_success_mean) %>% na.omit()
ggplot(data.resolution.ss,aes(Model_resolution_min,Settlement_success_mean)) + geom_point() 
ggplot(data.resolution.ss,aes(Nested_submodels,Settlement_success_mean)) + geom_boxplot()+ geom_jitter(width = 0.2)
```


##Biological models


###Pelagic larval durations
```{r}
ggplot(data.all,aes(x=PLD_fixed)) + geom_density()
data.all %>% group_by(PLD_type) %>% summarise (n = n()) %>% mutate(freq = n / sum(n)) %>% na.omit
```
####Comparisons
```{r}

data.all.lessoutlier <- filter(data.all,PLD_fixed < 150)

ggplot(data.all.lessoutlier,aes(PLD_fixed,Self_recruitment_mean)) + geom_point() 
ggplot(data.all.lessoutlier,aes(PLD_fixed,Local_retention_mean)) + geom_point()
ggplot(data.all.lessoutlier,aes(PLD_fixed,Settlement_success_mean)) + geom_point()
ggplot(data.all.lessoutlier,aes(PLD_fixed,Distance_travelled_mean)) + geom_point() 
```


###Mortality
```{r}
data.all %>% filter(Mortality == TRUE) %>% group_by(Mortality_function) %>% summarise (n = n()) %>% mutate(freq = n / sum(n))
ggplot(data.all, aes(Mortality, Self_recruitment_mean)) + geom_boxplot() + geom_jitter(width = 0.2)
ggplot(data.all, aes(Mortality, Local_retention_mean)) + geom_boxplot()+ geom_jitter(width = 0.2)
ggplot(data.all, aes(Mortality, Settlement_success_mean)) + geom_boxplot()+ geom_jitter(width = 0.2)
ggplot(data.all, aes(Mortality, Distance_travelled_mean)) + geom_boxplot()+ geom_jitter(width = 0.2)
```

###Sensory extent
```{r}
ggplot(data.all,aes(x=Sensory_extent)) + geom_density()
ggplot(data.all,aes(x=Sensory_extent,y=Self_recruitment_mean)) + geom_point()
ggplot(data.all,aes(x=Sensory_extent,y=Local_retention_mean)) + geom_point()
ggplot(data.all,aes(x=Sensory_extent,y=Settlement_success_mean)) + geom_point()
```

###Proportions of implemented behaviours
```{r}
data.all %>% group_by(Mortality) %>% summarise (n = n()) %>% mutate(freq = n / sum(n))
data.all %>% group_by(Growth) %>% summarise (n = n()) %>% mutate(freq = n / sum(n))
data.all %>% group_by(Sensory_ability) %>% summarise (n = n()) %>% mutate(freq = n / sum(n))
data.all %>% group_by(Settlement_competency_window) %>% summarise (n = n()) %>% mutate(freq = n / sum(n))
data.all %>% group_by(Orientation) %>% summarise (n = n()) %>% mutate(freq = n / sum(n))
```

###Proportions of swimming behaviours for ALL larvae
```{r}
larvae.swimming <- filter(data.all,Passive_movement==FALSE)
larvae.swimming %>% group_by(Horizontal_swimming_ability) %>% summarise (n = n()) %>% mutate(freq = n / sum(n))
larvae.swimming %>% group_by(Vertical_swimming_ability) %>% summarise (n = n()) %>% mutate(freq = n / sum(n))
larvae.swimming %>% group_by(Ontogentic_vertical_migration) %>% summarise (n = n()) %>% mutate(freq = n / sum(n))
larvae.swimming %>% group_by(Diel_vertical_migration) %>% summarise (n = n()) %>% mutate(freq = n / sum(n))
larvae.swimming %>% group_by(Halocline_migration) %>% summarise (n = n()) %>% mutate(freq = n / sum(n))
larvae.swimming %>% group_by(Circatidal_migration) %>% summarise (n = n()) %>% mutate(freq = n / sum(n))
larvae.swimming %>% group_by(Pynocline_migration) %>% summarise (n = n()) %>% mutate(freq = n / sum(n))
larvae.swimming %>% group_by(Sinking_velocity) %>% summarise (n = n()) %>% mutate(freq = n / sum(n))
larvae.swimming %>% group_by(Egg_buoyancy) %>% summarise (n = n()) %>% mutate(freq = n / sum(n))
```

##Comparisons

###Outputs with movement / settlement / orientation
```{r}
data.compare.metrics <- data.all %>% 
  mutate(settlement = Sensory_ability & Passive_movement & !Orientation) %>% 
  mutate(move_orien = movement & Orientation & !Sensory_ability) %>% 
  mutate(orien_settle = Orientation & Sensory_ability & Passive_movement) %>% 
  mutate(move_orien_settle = Orientation & Sensory_extent > 0 & !Passive_movement) %>% 
  mutate(move_settle = Sensory_ability & movement & !Orientation) %>% 
  mutate(no_behav = Passive_movement == TRUE & Sensory_ability == FALSE & Orientation == FALSE) %>% 
  mutate(orien = Orientation == TRUE & Sensory_ability == FALSE & Passive_movement == TRUE) %>% 
  mutate(move = Passive_movement == FALSE & Sensory_ability == FALSE & Orientation == FALSE)

data.compare.metrics <- data.compare.metrics %>% gather(Behaviours, Implemented, no_behav,move,orien,settlement,move_orien,orien_settle,move_settle,move_orien_settle) %>% filter(Implemented == TRUE)

data.compare.metrics$Behaviours <- factor(data.compare.metrics$Behaviours,levels = c('no_behav','move','orien','settlement','move_orien','move_settle','orien_settle','move_orien_settle'),ordered=TRUE)

ggplot(data.compare.metrics,aes(Behaviours,Self_recruitment_mean)) + geom_boxplot(na.rm = TRUE) + geom_jitter(width=0.2) 
ggplot(data.compare.metrics,aes(Behaviours,Local_retention_mean)) + geom_boxplot(na.rm = TRUE) + geom_jitter(width=0.2)
ggplot(data.compare.metrics,aes(Behaviours,Settlement_success_mean)) + geom_boxplot(na.rm = TRUE) + geom_jitter(width=0.2)
```

###Comparisons of different movement methods
```{r}
data.compare.moving <- data.all %>% gather(movement_factor, implemented,  Passive_movement, Circatidal_migration, Pynocline_migration, Halocline_migration, Ontogentic_vertical_migration, Vertical_swimming_ability, Horizontal_swimming_ability, Sinking_velocity, Diel_vertical_migration) %>% filter(implemented == TRUE)


ggplot(data.compare.moving,aes(movement_factor,Self_recruitment_mean)) + geom_boxplot(na.rm = TRUE) + geom_jitter(width=0.2) + coord_flip()
ggplot(data.compare.moving,aes(movement_factor,Local_retention_mean)) + geom_boxplot(na.rm = TRUE) + geom_jitter(width=0.2) + coord_flip()
ggplot(data.compare.moving,aes(movement_factor,Settlement_success_mean)) + geom_boxplot(na.rm = TRUE) + geom_jitter(width=0.2) + coord_flip()

ggplot(data.all,aes(Passive_movement,Self_recruitment_mean)) + geom_boxplot(na.rm = TRUE) + geom_jitter(width=0.2) + coord_flip()
ggplot(data.all,aes(Passive_movement,Local_retention_mean)) + geom_boxplot(na.rm = TRUE) + geom_jitter(width=0.2) + coord_flip()
ggplot(data.all,aes(Passive_movement,Settlement_success_mean)) + geom_boxplot(na.rm = TRUE) + geom_jitter(width=0.2) + coord_flip()
```

###Comparisons of different settlement methods
```{r}
data.compare.settlement <- data.all %>% mutate(settlement,Sensory_extent > 0)
ggplot(data.compare.settlement,aes(settlement,Self_recruitment_mean)) + geom_boxplot(na.rm = TRUE) + geom_jitter(width=0.2) 
ggplot(data.compare.settlement,aes(settlement,Local_retention_mean)) + geom_boxplot(na.rm = TRUE) + geom_jitter(width=0.2) 
ggplot(data.compare.settlement,aes(settlement,Settlement_success_mean)) + geom_boxplot(na.rm = TRUE) + geom_jitter(width=0.2) 
```

###Comparisons of different sensory extent sizes
```{r}
ggplot(data.compare.settlement, aes(Sensory_extent,Self_recruitment_mean)) + geom_point()
ggplot(data.compare.settlement, aes(Sensory_extent,Local_retention_mean)) + geom_point()
ggplot(data.compare.settlement, aes(Sensory_extent,Settlement_success_mean)) + geom_point()
```

###Comparisons of different sensory extent sizes
```{r}
data.compare.settlement <- data.all %>% select(Settlement_site_size,Sensory_extent,Self_recruitment_mean,Local_retention_mean,Settlement_success_mean, Sensory_impl)  %>%  mutate(settlement_size_normalised = if_else(Sensory_impl=="Buffer",(sqrt(Settlement_site_size)+Sensory_extent)^2,Settlement_site_size,missing=Settlement_site_size)) %>% filter(settlement_size_normalised > 0 & settlement_size_normalised < 500 )

ggplot(data.compare.settlement, aes(settlement_size_normalised,Self_recruitment_mean)) + geom_point()
ggplot(data.compare.settlement, aes(settlement_size_normalised,Local_retention_mean)) + geom_point()
ggplot(data.compare.settlement, aes(settlement_size_normalised,Settlement_success_mean)) + geom_point()
```

####Open / Closed
```{r}
ggplot(data.all,aes(System,Self_recruitment_mean)) + geom_boxplot(na.rm = TRUE) + geom_jitter(width=0.2) 
ggplot(data.all,aes(System,Local_retention_mean)) + geom_boxplot(na.rm = TRUE) + geom_jitter(width=0.2)
ggplot(data.all,aes(System,Settlement_success_mean)) + geom_boxplot(na.rm = TRUE) + geom_jitter(width=0.2)
```



####New settlement size
```{r}
data.all.size 
```