---
output:
  pdf_document: default
  html_document: default
---
# Analysis steps for empirical chapter

Two facets for each analysis, a total taxa trend for reef fish, and looking at the 7 individual families.

```{r, include=FALSE}
library("tidyverse")
library("lintr")
library("car")
```

Read in and tidy the data
```{r}
# The two data sets, one containing measuresments, the other tow information
data <- read_csv("../../data/ichthyoplankton-measurements.csv")
data.tow <- read_csv("../../data/ichthyoplankton-tow.csv")

# Select relevant columns
data <- filter(data, family != "bothid" & family != "triglid")
data <- filter(data, is.na(not_calibrated), is.na(damaged))
data <- select(data, -subgroup, -photo_id, -damaged, -not_calibrated)

# Create factors (tibble does not import as factors)
data$stage <- factor(data$stage, levels = c("PRE", "FLE", "POS"))
data$family <- as.factor(data$family)
data$net <- as.factor(data$net)
data$depth <- as.factor(data$depth)
data$preservation_method <- as.factor(data$preservation_method)
data$feature <- as.factor(data$feature)
data$location <- as.factor(data$location)
data$station <- as.factor(data$station)
data$site <- as.factor(data$site)
data.tow$net <- as.factor(data.tow$net_number)
data.tow$feature <- as.factor(data.tow$feature)
data.tow$feature_name <- as.factor(data.tow$feature_name)
data.tow$location <- as.factor(data.tow$location)
data.tow$site <- as.factor(data.tow$site)
data.tow$station <- as.factor(data.tow$station)

# Calculate total length from the standard length and the caudal fin length
data.length.raw <- mutate(data, total_length = standard_length + caudal_fin_length)

# Get the raw counts for each stage per net (needed to calculate concentration)
data.stage <- summarize(group_by(data, location, station, feature, net, family,
                               stage), count = n())

# Organise the data to have zero counts where there was no data
data.spread <- spread(data.stage, key=stage, value=count, drop =FALSE, fill = 0)
data.gather <- gather(data.spread, key=stage, value=count, PRE, POS, FLE, na.rm = FALSE)

# Calculate the concetration as 1000 cubic metres and balance the data
data.conc <- data.gather %>% left_join(data.tow) %>% mutate(conc = count/volume * 1000) %>% filter(site != "4", site != "8", site != "12", site != "16")

# Transform the data by log(x + 1) as there are zeros, and add depth column for net
data.conc <- mutate(data.conc, conc_log = log(conc + 1),
      depth = if_else(net == 'N1' || net == 'N2', 0, if_else(net == 'M5' || net == 'M4', 25 ,75)))
data.conc$depth <- as.factor(data.conc$depth)

# Get the mean concentration for each net
data.summary.total <- summarise(group_by(data.conc, location, feature, depth, stage), sum_conc=sum(conc_log), mean_conc = mean(conc), sd_conc = sd(conc), mean_conc_log = mean(conc_log), sd_conc_log = sd(conc_log))

# Get the mean length for each net
data.length.sum <- summarize(group_by(data.length.raw, location, feature, depth, family), length_mean = mean(total_length), length_sd = sd(total_length), length_se = length_sd/n())

```


## Aim 1: Does stage predict depth

The design of the experiment is unbalanced, as we lost one surface tow at site 8 to a broken logger and we lost one surface tow at site 16 to rough weather. Therefore to balance the design up, I removed the incomplete sites, and two other sites. Thus for the concentration analysis it has 12 sites instead of 16.

**Hypothesis**: The stage of the fish will have an effect on the depth of the reef fish.
**Null hypothesis**: There will be no effect of stage on depth for reef fish.

### Exploratory graphs

Graph concentration as a factor of stage, grouped by depth


```{r}
ggplot(aes(x=depth, y=conc_log), data=data.conc) + geom_boxplot()
```

#### Site differences

The SST is greater at the north

```{r}
ggplot(aes(x=location, y=sst), data=data.tow) + geom_boxplot()
t.test(sst~location,data=data.tow)
```

The salinity was more varied in the north, and the mean slightly lower, but significantly different.

```{r}
ggplot(aes(x=location, y=salinity), data=data.tow) + geom_boxplot()
t.test(salinity~location,data=data.tow)
```

The cholorophyll fluorescence was significantly higher in the southern waters

```{r}
ggplot(aes(x=location, y=chlorophyll_fluorescence), data=data.tow) + geom_boxplot()
t.test(chlorophyll_fluorescence~location,data=data.tow)
```

### Model

The factors chosen:
- Location. They were at different latitudes, so there are sst / salinty / chlorophyll differences (and I'm sure more variables)
- Feature. The water type was either from coastal source water or from inside an eddy
- Depth. The three depths the fish were caught at.
- Stage. The three stages of ontogeny the fish were measured at


| Independent factors | Type   | Levels | Nested | Values                             |
|:--------------------|:-------|:-------|:-------|------------------------------------|
| location            | fixed  | 2      | no     | north, south                       |
| feature             | fixed  | 2      | no     | coastal, eddy                      |
| depth               | fixed  | 3      | no     | 0, 25, 75                          |
| stage               | fixed  | 3      | no     | pre-flexion, flexion, post-flexion |

Unit of replication = net (2) * site(3) = 6

| Dependent factor | Transformation | Units |
|:-----------------|:---------------|:------|
| Concentration    | log(x+1)       | 1000m^3|

Transformation as per Underwood for concentration data. Also x1000 to get concentrations at 1000m^3. The idea of increasing it was get large enough values so the logarithm transformation was monotomic. Plotting the mean and sd before and after the log transformation.

```{r}
ggplot(data = data.summary.total, aes(x = mean_conc, y = sd_conc)) + geom_point()
ggplot(data = data.summary.total, aes(x = mean_conc_log, y = sd_conc_log)) + geom_point()
```

### Total reef fish ontogeny

Measures the overall trends for the reef fish, regardless of taxa. Location, feature, depth and stage are all significant. Including many interactions (and the 5-way interaction).

```{r}
model.conc <- lm(conc_log ~ location * feature * depth * stage * family, data=data.conc)
Anova(model.conc, type = "II")
```

Splitting family up into each taxa after the significant 5-way interaction

### Labridae

Labrids have a significant differences across all the main effects and the 4-way interaction.

```{r}
data.conc.labrid <- filter(data.conc, family == "labridae")
model.conc.labrid <- lm(conc_log ~ location * feature * depth * stage, data=data.conc.labrid)
Anova(model.conc.labrid, type = "II")
```

### Mullidae

Mullids have a significant main effect of feature and depth, and also the 4-way interaction.

```{r}
data.conc.mullid <- filter(data.conc, family == "mullidae")
model.conc.mullid <- lm(conc_log ~ location * feature * depth * stage, data=data.conc.mullid)
Anova(model.conc.mullid, type = "II")
```

### Pomcentridae

Pomacentrids have a significant differences in depth and stage, and also the 4-way interaction.

```{r}
data.conc.pom <- filter(data.conc, family == "pomacentridae")
model.conc.pom <- lm(conc_log ~ location * feature * depth * stage, data=data.conc.pom)
Anova(model.conc.pom, type = "II")
```

### Scaridae

Scarids have significants main effects of location, feature, & stage. The main signification interation (using 0.001 as a cut off), are feature and stage, location and depth and location and feature. The was no significant interaction of depth & stage.

```{r}
data.conc.scarid <- filter(data.conc, family == "scaridae")
model.conc.scarid <- lm(conc_log ~ location * feature * depth * stage, data=data.conc.scarid)
Anova(model.conc.scarid, type = "II")
```

### Scorpaenidae

The main effects of location, depth and feature are significant. As well as the interactions of location x feature x stage and also feature x depth x stage.
```{r}
data.conc.scorp <- filter(data.conc, family == "scorpaenidae")
model.conc.scorp <- lm(conc_log ~ location * feature * depth * stage, data=data.conc.scorp)
Anova(model.conc.scorp, type = "II")
```

### Serranidae

There is a significant main effect of stage and an interaction term of location x feature x stage.

```{r}
data.conc.serr <- filter(data.conc, family == "serranidae")
model.conc.serr <- lm(conc_log ~ location * feature * depth * stage, data=data.conc.serr)
Anova(model.conc.serr, type = "II")
```

### Synodontidae

The main effects of location and depth have significant effects. All of the 3-way interactions are significant for sydnodontids.

```{r}
data.conc.syn <- filter(data.conc, family == "synodontidae")
model.conc.syn <- lm(conc_log ~ location * feature * depth * stage, data=data.conc.syn)
Anova(model.conc.syn, type = "II")
```

## Aim 2: Does length predict depth

| Independent factors | Type   | Levels | Values                             |
|:--------------------|:-------|:-------|------------------------------------|
| location            | fixed | 2      | north, south                       |
| feature             | fixed  | 2      | coastal, eddy                      |
| depth              | fixed  | 3      | 0, 25, 75                          |

| Dependent factor | Transformation | Units |
|:-----------------|:---------------|:------|
| Total length    | log(x)       | mm |

Log transformation was applied to the size data to normalise the distribution.

### Total reef fish length

The model explained 50% of the data. The 3-way interactions of location:feature:depth, location:feature:family and location:depth:family were all significant. All of the main effects were also significant. Therefore it is hard to determine what is the effect of location / feature / depth on the length of the fish.

```{r}
data.length.raw <- mutate(data.length.raw, length_transform = log(total_length))
ggplot(aes(total_length),data=data.length.raw) + geom_density()
ggplot(aes(length_transform),data=data.length.raw) + geom_density()
model.length <- lm(length_transform ~ location * feature * depth, data=data.length.raw)
Anova(model.length, type="III", singular.ok = TRUE)
summary(model.length)
```

### Labridae

Labrids have a strong significant main effect of both location and depth, and a weaker significance at feature. There was a 3-way interaction between location x feature x depth.

```{r}
data.length.labrid <- filter(data.length.raw, family == "labridae")
model.length.labrid <- lm(total_length ~ location * feature * depth, data=data.length.labrid)
Anova(model.length.labrid, type="III")
summary(model.length.labrid)
```

### Mullidae

Mullids only had a significant effect at feature, suggesting the type of water body influences the length of the mullids.

Note that mullids had singularities in the southern eddy because of low or zero catch numbers.

```{r}
data.length.mullid <- filter(data.length.raw, family == "mullidae")
model.length.mullid <- lm(length_transform ~ location * feature * depth, data=data.length.mullid)
Anova(model.length.mullid, type="III", singular.ok = TRUE)
summary(model.length.mullid)
alias(model.length.mullid)
data.length.mullid.sum <- summarise(group_by(data.length.mullid, feature), mean_len=mean(total_length),sd_len =sd(total_length),se_len=sd(total_length)/n())
ggplot(data=data.length.mullid.sum, aes(x=feature,y=mean_len)) + geom_col() + geom_errorbar(aes(ymin=mean_len-se_len, ymax=mean_len+se_len),width=0.1)
```

### Pomcentridae
Note that pomacentirds had singularities in the southern eddy because of low or zero catch numbers. This agan makes it hard to interpret the data having signification effects  at the interations of location:feature. More so location and depth, suggesting that other factors influence depth other than length.

```{r}
data.length.pom <- filter(data.length.raw, family == "pomacentridae")
model.length.pom <- lm(length_transform ~ location * feature * depth, data=data.length.pom)
alias(model.length.pom)
Anova(model.length.pom, type="III", singular.ok = TRUE)
summary(model.length.pom)
```

### Scaridae

Again, low numbers in the southern eddy.


```{r}
data.length.scarid <- filter(data.length.raw, family == "scaridae")
model.length.scarid <- lm(length_transform ~ location * feature * depth, data=data.length.scarid)
alias(model.length.scarid)
Anova(model.length.scarid, type="III", singular.ok = TRUE)
summary(model.length.scarid)
```

### Scorpaenidae

Significant interaction at location and depth.
```{r}
data.length.scorp <- filter(data.length.raw, family == "scorpaenidae")
model.length.scorp <- lm(length_transform ~ location * feature * depth, data=data.length.scorp)
Anova(model.length.scorp, type ="III")
```

### Serranidae

For serranids, location and feature have a significant interaction, and all the main effects.

```{r}
data.length.serr <- filter(data.length.raw, family == "serranidae")
model.length.serr <- lm(length_transform ~ location * feature * depth, data=data.length.serr)
Anova(model.length.serr, type="III")
```

### Synodontidae

Again low counts in the southern eddy, but feature is seen as a significant effect on the length of the fish.

```{r}
data.length.syn <- filter(data.length.raw, family == "synodontidae")
model.length.syn <- lm(length_transform ~ location * feature * depth, data=data.length.syn)
alias(model.length.syn)
Anova(model.length.syn, type="III", singular.ok = TRUE)

data.length.syn.sum <- summarise(group_by(data.length.syn, feature), mean_len=mean(total_length),sd_len =sd(total_length),se_len=sd(total_length)/n())
ggplot(data=data.length.syn.sum, aes(x=feature,y=mean_len)) + geom_col() + geom_errorbar(aes(ymin=mean_len-se_len, ymax=mean_len+se_len),width=0.1)

```

## Outcomes

### Ontogeny
The location of fish in the water column is not simply a factor of ontoegentic stage. While the interaction of the two is significant, it is hard to determine the strength of the interaction due to the significance of other factors such as location and water feature.


### Length
Feature seems to be more of a predictor of larval reef fish length than depth, especially for Synodontids and Mullids. Although the unbalanced data collection means we have to be careful with the interpretation.

## Caveats

- The depths we used (very broad, similar analyses didnt even compare Neuston vs MOCHNESS as can catch different fish)
- The age of eddies were different, one was an old eddy (northern site) and the other was a younger eddy (southern site)
- Catching schools over individuals could influence results
- Unbalanced sampling
