---
title: "Linear mixed model analysis for concentration as factor of ontogeny"
output:
  pdf_document: default
  html_notebook: default
---

```{r, include=FALSE}
require(tidyverse)
require(car)
require(MASS)
require(lmerTest)
require(lme4)
require(lsmeans)
```


The data is not normally distributed (log normal distribution). 

SEE: https://stats.stackexchange.com/questions/181034/post-hoc-test-of-interaction-factor-in-binomial-glmm-with-proportions
https://cran.r-project.org/web/packages/lsmeans/vignettes/using-lsmeans.pdf

Read in and tidy the data
```{r}
# The two data sets, one containing measuresments, the other tow information
data <- read_csv("../../data/ichthyoplankton-measurements.csv")
data.tow <- read_csv("../../data/ichthyoplankton-tow.csv")

# Select relevant columns
data <- filter(data, family != "bothid" & family != "triglid")
data <- filter(data, is.na(not_calibrated), is.na(damaged))
data <- dplyr::select(data, -subgroup, -photo_id, -damaged, -not_calibrated)

# Create factors (tibble does not import as factors)
data$stage <- factor(data$stage, levels = c("PRE", "FLE", "POS"))
data$family <- as.factor(data$family)
data$net <- as.factor(data$net)
data$depth <- as.factor(data$depth)
data$preservation_method <- as.factor(data$preservation_method)
data$feature <- as.factor(data$feature)
data$location <- as.factor(data$location)
data$station <- as.factor(data$station)
data$site <- as.factor(data$site)
data.tow$net <- as.factor(data.tow$net_number)
data.tow$feature <- as.factor(data.tow$feature)
data.tow$feature_name <- as.factor(data.tow$feature_name)
data.tow$location <- as.factor(data.tow$location)
data.tow$site <- as.factor(data.tow$site)
data.tow$station <- as.factor(data.tow$station)

# Get the raw counts for each stage per net (needed to calculate concentration)
data.stage <- summarize(group_by(data, location, station, feature, net, family,
                               stage), count = n())

# Organise the data to have zero counts where there was no data
data.spread <- spread(data.stage, key=stage, value=count, drop =FALSE, fill = 0)
data.gather <- gather(data.spread, key=stage, value=count, PRE, FLE, POS,  na.rm = FALSE)

# Calculate the concetration as 1000 cubic metres and balance the data
data.conc <- data.gather %>% left_join(data.tow) %>% mutate(conc = count/volume * 250)
#data.conc$stage <- as.factor(data$data.conc, levels = c("PRE", "FLE", "POS"))

# Transform the data by log(x + 1) as there are zeros, and add depth column for net
data.conc <- mutate(data.conc, conc_log = log(conc + 1),
      depth = if_else(net == 'N1' || net == 'N2', 0, if_else(net == 'M5' || net == 'M4', 25 ,75)))
data.conc$depth <- as.factor(data.conc$depth)
data.conc <- mutate(data.conc, conc.t = conc + 1)
```


# The Model

The factors chosen:
- Location. They were at different latitudes, so there are sst / salinty / chlorophyll differences (and I'm sure more variables)
- Feature. The water type was either from coastal source water or from inside an eddy
- Station. 3 stations within a feature
- Depth. The three depths the fish were caught at.
- Stage. The three stages of ontogeny the fish were measured at


| Independent factors | Type   | Levels | Nested | Values                             |
|:--------------------|:-------|:-------|:-------|:-----------------------------------|
| location            | random | 2      | no     | NA                                 |
| feature             | fixed  | 2      | no     | coastal, eddy                      |
| station             | random | 3      | yes    | NA                                 |
| depth               | fixed  | 3      | no     | 0, 25, 75                          |
| stage               | fixed  | 3      | no     | pre-flexion, flexion, post-flexion |

Unit of replication = 2 (net)

| Dependent factor | Transformation | Units |
|:-----------------|:---------------|:------|
| Concentration    | log(x+1)       | 250m^3|

Transformation as per Underwood for concentration data. Also x1000 to get concentrations at 250m^3. The idea of increasing it was get large enough values so the logarithm transformation was monotomic. Plotting the mean and sd before and after the log transformation.


# Labrid

```{r}
labrid.data <- filter(data.conc, family == "labridae")
qqp(labrid.data$conc, "norm")
```

## Model
```{r}
labrid.lme <- lmer(conc_log ~ feature * depth * stage + (1 | location) + (1 | feature : station), data=labrid.data)
summary(labrid.lme)
```

## Anova
```{r}
Anova(labrid.lme)
```

## Interaction diagram
```{r}
lsmip(labrid.lme, stage ~ depth | feature)
lsmip(labrid.lme, stage ~ feature)
lsmip(labrid.lme, depth ~ feature)
lsmip(labrid.lme, stage ~ depth)
```

## Post-hoc tests

So there was no interaction driven by stage and depth. There were interactions, driven by the differences between feature. Most labrids tend to live in the top 50m. The was in increase of concentration of pre-flexion and flexion labrids in the eddy.

### Feature x Stage Interaction
```{r}
lsmeans::lsmeans(labrid.lme, ~ feature*stage)
summary(pairs(lsmeans::lsmeans(labrid.lme, ~ feature*stage)), type = "response")
```

####Feature x Depth Interaction
```{r}
lsmeans(labrid.lme, ~ feature*depth)
summary(pairs(lsmeans(labrid.lme, ~ feature*depth)), type = "response")
```


# Mullid
```{r}
mullid.data <- filter(data.conc, family == "mullidae")
```

## Model
```{r}
mullid.lme <- glmer(conc.t ~ feature * depth * stage + (1 | location) + (1 | feature : station), family=gaussian(link="log"), data=mullid.data, REML = FALSE)
summary(mullid.lme)
```
## Anova
```{r}
Anova(mullid.lme)
```

## Interaction diagram
```{r}
lsmip(mullid.lme, stage ~ depth | feature)
lsmip(mullid.lme, stage ~ depth)
lsmip(mullid.lme, stage ~ feature)
```

## Post-hoc tests

### Depth x Stage
```{r}
lsmeans(mullid.lme, ~ stage * depth)
summary(pairs(lsmeans(mullid.lme, ~ stage * depth)), type = "response")
```

### Feature x Stage
```{r}
lsmeans(mullid.lme, ~ stage * feature)
summary(pairs(lsmeans(mullid.lme, ~ stage * feature)), type = "response")
```

# Pomacentridae
```{r}
pomacentrid.data <- filter(data.conc, family == "pomacentridae")
```

## Model
```{r}
pomacentrid.lme <- lmer(conc_log ~ feature * depth * stage + (1 | location) + (1 | feature : station), data=pomacentrid.data, REML = FALSE)
summary(pomacentrid.lme)
```

## Anova
```{r}
Anova(pomacentrid.lme)
```

## Interaction diagram
```{r}
lsmip(pomacentrid.lme, stage ~ depth | feature)
lsmip(pomacentrid.lme, stage ~ depth)
```


## Post-hoc

### Stage
```{r}
lsmeans(pomacentrid.lme, ~ stage)
summary(pairs(lsmeans(pomacentrid.lme, ~ stage)), type = "response")
```

### Depth
```{r}
lsmeans(pomacentrid.lme, ~ depth)
summary(pairs(lsmeans(pomacentrid.lme, ~ depth)), type = "response")
```

# Scaridae
```{r}
scarid.data <- filter(data.conc, family == "scaridae")
```

## Model
```{r}
scarid.lme <- lmer(conc_log ~ feature * depth * stage + (1 | location) + (1 | feature : station), data=scarid.data, REML=FALSE)
summary(scarid.lme)
```

## Anova
```{r}
Anova(scarid.lme)
```

## Interaction diagram
```{r}
lsmip(scarid.lme, stage ~ depth | feature)
```

## Post-hoc tests

### 3-way interaction
```{r}
lsmeans(scarid.lme, ~ stage * depth * feature)
summary(pairs(lsmeans(scarid.lme, ~ stage * depth * feature)), type = "response")
```

# Scorpionfish
```{r}
scorpaenid.data <- filter(data.conc, family == "scorpaenidae")
```

## Distribution
```{r}
scorpaenid.data$conc.t <- scorpaenid.data$conc + 1
qqp(scorpaenid.data$conc.t, "lnorm")
```

## Model
```{r}
scorpaenid.glmm <- glmer(conc.t ~ feature * depth * stage + (1 | location) + (1 | feature : station), family=gaussian(link="log"), data=scorpaenid.data, control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
summary(scorpaenid.glmm)
```

## Anova
```{r}
Anova(scorpaenid.glmm)
```

## Interaction diagram
```{r}
lsmip(scorpaenid.glmm, stage ~ depth | feature)
lsmip(scorpaenid.glmm, stage ~ feature)
```

## Post-hoc tests

### Feature x Depth x Stage Interaction
```{r}
lsmeans(scorpaenid.glmm, ~ feature*depth*stage)
summary(pairs(lsmeans(scorpaenid.glmm, ~ feature*depth*stage)), type = "response")
```

# Lizardfish
```{r}
synodontid.data <- filter(data.conc, family == "synodontidae")
```

## Model
```{r}
synodontid.lme <- lmer(conc_log ~ feature * depth * stage + (1 | location) + (1 | feature : station), data=synodontid.data, REML=FALSE)
summary(synodontid.lme)
```

## Anova
```{r}
Anova(synodontid.lme)
```

## Interaction diagram
```{r}
lsmip(synodontid.lme, stage ~ feature)
lsmip(synodontid.lme, stage ~ depth)
```

## Post-hoc tests

### Feature x Stage Interaction
```{r}
lsmeans(synodontid.lme, ~ feature*stage)
summary(pairs(lsmeans(synodontid.lme, ~ feature*stage)), type = "response")
```

# Parrotfish
```{r}
serranid.data <- filter(data.conc, family == "serranidae")
```


## Model
```{r}
serranid.lme <- lmer(conc_log ~ feature * depth * stage + (1 | location) + (1 | feature : station), data=serranid.data, REML = FALSE)
summary(serranid.lme)
```

## Anova
```{r}
Anova(serranid.lme)
```

## Interaction diagram
```{r}
lsmip(serranid.lme, stage ~ depth)
```

## Post-hoc tests

### Depth x Stage Interaction
```{r}
lsmeans(serranid.lme, ~ depth*stage)
summary(pairs(lsmeans(serranid.lme, ~ depth*stage)), type = "response")
```
