---
title: "Linear mixed model analysis for concentration as factor of ontogeny"
output:
  pdf_document: default
  html_notebook: default
---

```{r, include=FALSE}
require(tidyverse)
require(car)
require(MASS)
require(lmerTest)
require(lme4)
require(lsmeans)
```


The data is not normally distributed (log normal distribution). 

SEE: https://stats.stackexchange.com/questions/181034/post-hoc-test-of-interaction-factor-in-binomial-glmm-with-proportions
https://cran.r-project.org/web/packages/lsmeans/vignettes/using-lsmeans.pdf

Read in and tidy the data
```{r}
# The two data sets, one containing measuresments, the other tow information
data <- read_csv("../../data/ichthyoplankton-measurements.csv")
data.tow <- read_csv("../../data/ichthyoplankton-tow.csv")

# Select relevant columns
data <- filter(data, family != "bothid" & family != "triglid")
data <- filter(data, is.na(not_calibrated), is.na(damaged))
data <- dplyr::select(data, -subgroup, -photo_id, -damaged, -not_calibrated)

# Create factors (tibble does not import as factors)
data$stage <- factor(data$stage, levels = c("PRE", "FLE", "POS"))
data$family <- as.factor(data$family)
data$net <- as.factor(data$net)
data$depth <- as.factor(data$depth)
data$preservation_method <- as.factor(data$preservation_method)
data$feature <- as.factor(data$feature)
data$location <- as.factor(data$location)
data$station <- as.factor(data$station)
data$site <- as.factor(data$site)
data.tow$net <- as.factor(data.tow$net_number)
data.tow$feature <- as.factor(data.tow$feature)
data.tow$feature_name <- as.factor(data.tow$feature_name)
data.tow$location <- as.factor(data.tow$location)
data.tow$site <- as.factor(data.tow$site)
data.tow$station <- as.factor(data.tow$station)

# Get the raw counts for each stage per net (needed to calculate concentration)
data.stage <- summarize(group_by(data, location, station, feature, net, family,
                               stage), count = n())

# Organise the data to have zero counts where there was no data
data.spread <- spread(data.stage, key=stage, value=count, drop =FALSE, fill = 0)
data.gather <- gather(data.spread, key=stage, value=count, PRE, FLE, POS,  na.rm = FALSE)

# Calculate the concetration as 1000 cubic metres and balance the data
data.conc <- data.gather %>% left_join(data.tow) %>% mutate(conc = count/volume)
#data.conc$stage <- as.factor(data$data.conc, levels = c("PRE", "FLE", "POS"))

# Transform the data by log(x + 1) as there are zeros, and add depth column for net
data.conc <- mutate(data.conc, conc_log = log(conc + 1),
      depth = if_else(net == 'N1' || net == 'N2', 0, if_else(net == 'M5' || net == 'M4', 25 ,75)))
data.conc$depth <- as.factor(data.conc$depth)
data.conc <- mutate(data.conc, conc.t = conc + 1)
data.conc <- mutate(data.conc, presence = ifelse(conc > 0, TRUE , FALSE))
```


# The Model

The factors chosen:
- Location. They were at different latitudes, so there are sst / salinty / chlorophyll differences (and I'm sure more variables)
- Feature. The water type was either from coastal source water or from inside an eddy
- Station. 3 stations within a feature
- Depth. The three depths the fish were caught at.
- Stage. The three stages of ontogeny the fish were measured at


| Independent factors | Type   | Levels | Nested | Values                             |
|:--------------------|:-------|:-------|:-------|:-----------------------------------|
| location            | random | 2      | no     | NA                                 |
| feature             | fixed  | 2      | no     | coastal, eddy                      |
| station             | random | 3      | yes    | NA                                 |
| depth               | fixed  | 3      | no     | 0, 25, 75                          |
| stage               | fixed  | 3      | no     | pre-flexion, flexion, post-flexion |

Unit of replication = 2 (net)

| Dependent factor | Transformation | Units |
|:-----------------|:---------------|:------|
| Concentration    | log(x+1)       | 250m^3|

Transformation as per Underwood for concentration data. Also x250 to get concentrations at 250m^3. The idea of increasing it was get large enough values so the logarithm transformation was monotomic. Plotting the mean and sd before and after the log transformation.


# Labrid

```{r}
labrid.data <- filter(data.conc, family == "labridae")
labrid.data.nonzero <- filter(labrid.data, conc > 0)
qqp(labrid.data.nonzero$conc, "lnorm")
```

## Model GLMM
```{r}
labrid.glmm.nonzero <- glmer(conc ~ feature * depth * stage + (1 | location) + (1 | feature : station), family=gaussian(link="log"),control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)), data=labrid.data.nonzero)
labrid.glmm.bernoulli <- glmer(presence ~ feature * depth * stage + (1 | location) + (1 | feature : station), family=binomial, data=labrid.data)
summary(labrid.glmm.nonzero)
summary(labrid.glmm.bernoulli)
```

## Model GLM
```{r}
labrid.glm.nonzero <- glm(conc ~ feature * depth * stage + temperature + salinity + chlorophyll_fluorescence, family=gaussian(link="log"), data=labrid.data.nonzero)
labrid.glm.zero <- glm(presence ~ feature * depth * stage + temperature + salinity + chlorophyll_fluorescence, family=binomial, data=labrid.data)
summary(labrid.glm.zero)
summary(labrid.glm.nonzero)
```

## Anova
```{r}
Anova(labrid.glmm)
```

## Interaction diagram
```{r}
lsmip(labrid.glmm, stage ~ depth | feature)
lsmip(labrid.glmm, stage ~ feature)
lsmip(labrid.glmm, depth ~ feature)
lsmip(labrid.glmm, stage ~ depth)
```

## Post-hoc tests

No post-hoc tests as no significance. 

# Mullid
```{r}
mullid.data <- filter(data.conc, family == "mullidae")
mullid.data.nonzero <- filter(mullid.data, conc > 0)
```

# Distribution
```{r}
qqp(mullid.data.nonzero$conc, "lnorm")
```

## Model
```{r}
mullid.glm.nonzero <- glm(conc ~ feature * depth * stage + temperature + salinity + chlorophyll_fluorescence, family=gaussian(link="log"), data=mullid.data.nonzero)
mullid.glm.zero <- glm(presence ~ feature * depth * stage + temperature + salinity + chlorophyll_fluorescence, family=binomial, data=mullid.data)
summary(mullid.glm.zero)
summary(mullid.glm.nonzero)
```

## Anova
```{r}
Anova(mullid.glmm.nonzero)
Anova(mullid.glmm.bernoulli)
```

## Interaction diagram
```{r}
lsmip(mullid.glmm.nonzero, stage ~ depth | feature)
lsmip(mullid.glmm.nonzero, feature ~ depth)
lsmip(mullid.glmm.nonzero, stage ~ feature)
```
## Interaction diagram
```{r}
lsmip(mullid.glmm.bernoulli, stage ~ depth | feature)
lsmip(mullid.glmm.bernoulli, stage ~ depth)
lsmip(mullid.glmm.bernoulli, stage ~ feature)
```

## Post-hoc tests

### Depth x Stage
```{r}
lsmeans(mullid.glmm.nonzero, ~ stage * depth * feature)
summary(pairs(lsmeans(mullid.glmm.nonzero, ~ stage * depth)), type = "response")
```


# Pomacentridae
```{r}
pomacentrid.data <- filter(data.conc, family == "pomacentridae")
pomacentrid.data.nonzero <- filter(pomacentrid.data, conc > 0)
qqp(pomacentrid.data.nonzero$conc, "lnorm")
```

## Model
```{r}
pomacentrid.glm.nonzero <- glm(conc ~ feature * depth * stage + temperature + salinity + chlorophyll_fluorescence, family=gaussian(link="log"), data=pomacentrid.data.nonzero)
pomacentrid.glm.zero <- glm(presence ~ feature * depth * stage + temperature + salinity + chlorophyll_fluorescence, family=binomial, data=pomacentrid.data)
summary(pomacentrid.glm.zero)
summary(pomacentrid.glm.nonzero)
```

## Anova
```{r}
Anova(pomacentrid.lme)
```

## Interaction diagram
```{r}
lsmip(pomacentrid.lme, stage ~ depth | feature)
lsmip(pomacentrid.lme, stage ~ depth)
```


## Post-hoc

### Stage
```{r}
lsmeans(pomacentrid.lme, ~ stage)
summary(pairs(lsmeans(pomacentrid.lme, ~ stage)), type = "response")
```

### Depth
```{r}
lsmeans(pomacentrid.lme, ~ depth)
summary(pairs(lsmeans(pomacentrid.lme, ~ depth)), type = "response")
```

# Scaridae
```{r}
scarid.data <- filter(data.conc, family == "scaridae" & conc != "NA")
scarid.data.nonzero <- filter(scarid.data, conc > 0)
qqp(scarid.data.nonzero$conc, "lnorm")
```

## Model
```{r}
scarid.glm.nonzero <- glm(conc ~ feature * depth * stage + temperature + salinity + chlorophyll_fluorescence, family=gaussian(link="log"), data=scarid.data.nonzero)
scarid.glm.zero <- glm(presence ~ feature * depth * stage + temperature + salinity + chlorophyll_fluorescence, family=binomial, data=scarid.data)
summary(scarid.glm.zero)
summary(scarid.glm.nonzero)
```

## Anova
```{r}
Anova(scarid.glmm)
```

## Interaction diagram
```{r}
lsmip(scarid.glm.zero, stage ~ depth)
lsmip(scarid.glm.nonzero, stage ~ depth)
lsmip(scarid.glm.nonzero, stage ~ feature)
```

## Post-hoc tests

### 3-way interaction
```{r}
lsmeans(scarid.glm.zero, ~ depth)
summary(pairs(lsmeans(scarid.glm.zero, ~ depth)), type = "response")
```

# Scorpionfish
```{r}
scorpaenid.data <- filter(data.conc, family == "scorpaenidae")
scorpaenid.data.nonzero <- filter(scorpaenid.data, conc > 0)
qqp(scorpaenid.data.nonzero$conc, "lnorm")
```

## Distribution
```{r}
qqp(scorpaenid.data$conc.t, "lnorm")
qqp(scorpaenid.data$conc_log, "norm")
```

## Model
```{r}
scorpaenid.glm.nonzero <- glm(conc ~ feature * depth * stage + temperature + salinity + chlorophyll_fluorescence, family=gaussian(link="log"), data=scorpaenid.data.nonzero)
scorpaenid.glm.zero <- glm(presence ~ feature * depth * stage + temperature + salinity + chlorophyll_fluorescence, family=binomial, data=scorpaenid.data)
summary(scorpaenid.glm.zero)
summary(scorpaenid.glm.nonzero)
```

## Anova
```{r}
Anova(scorpaenid.glmm)
```

## Interaction diagram
```{r}
lsmip(scorpaenid.glm.zero, stage ~ depth | feature)
lsmip(scorpaenid.glm.zero, stage ~ depth)
lsmip(scorpaenid.glm.nonzero, stage ~ depth | feature)
lsmip(scorpaenid.glm.nonzero, stage ~ depth)
```

## Post-hoc tests

### Feature x Depth x Stage Interaction
```{r}
lsmeans(scorpaenid.glmm, ~ feature*depth*stage)
summary(pairs(lsmeans(scorpaenid.glmm, ~ feature*depth*stage)), type = "response")
```

# Lizardfish
```{r}
synodontid.data <- filter(data.conc, family == "synodontidae")
synodontid.data.nonzero <- filter(synodontid.data, conc > 0)
qqp(synodontid.data.nonzero$conc, "lnorm")
```

## Model
```{r}
synodontid.glm.nonzero <- glm(conc ~ feature * depth * stage + temperature + salinity + chlorophyll_fluorescence, family=gaussian(link="log"), data=synodontid.data.nonzero)
synodontid.glm.zero <- glm(presence ~ feature * depth * stage + temperature + salinity + chlorophyll_fluorescence, family=binomial, data=synodontid.data)
summary(synodontid.glm.zero)
summary(synodontid.glm.nonzero)
```

## Anova
```{r}
Anova(synodontid.glmm)
```

## Interaction diagram
```{r}
lsmip(synodontid.glmm, stage ~ feature)
lsmip(synodontid.glmm, stage ~ depth)
```

## Post-hoc tests

### Feature x Stage Interaction
```{r}
lsmeans(synodontid.glmm, ~ feature*stage)
summary(pairs(lsmeans(synodontid.glmm, ~ feature*stage)), type = "response")
```

# Parrotfish
```{r}
serranid.data <- filter(data.conc, family == "serranidae" & conc.t != "NA")
serranid.data.nonzero <- filter(serranid.data, conc > 0)
qqp(serranid.data.nonzero$conc, "lnorm")
```


## Model
```{r}
serranid.glm.nonzero <- glm(conc ~ feature * depth * stage + temperature + salinity + chlorophyll_fluorescence, family=gaussian(link="log"), data=serranid.data.nonzero)
serranid.glm.zero <- glm(presence ~ feature * depth * stage + temperature + salinity + chlorophyll_fluorescence, family=binomial, data=serranid.data)
summary(serranid.glm.zero)
summary(serranid.glm.nonzero)
```

## Anova
```{r}
Anova(serranid.glm.nonzero, type = "3")
```

## Interaction diagram
```{r}
lsmip(serranid.glm.zero, stage ~ depth)
lsmip(serranid.glm.nonzero, stage ~ depth)
```

## Post-hoc tests

### Depth x Stage Interaction
```{r}
lsmeans(serranid.glm.zero, ~ depth*stage)
summary(pairs(lsmeans(serranid.glm.zero, ~ depth*stage)), type = "response")
```
