---
title: "Literature review analysis"
output:
  html_document: default
  html_notebook: default
---


```{r include=FALSE}
# Load libraries
library("grid")
library("gridExtra")
library("tidyverse")
library("ggthemes")
library("lsmeans")
library("multcompView")
library("car")

# Load external functions
source("sort_factor.R")
source("get_factor_proportion.R")
source("multiplot.R")
```

Load the data from the .csv file
```{r include=FALSE}
#check the columns loaded
data.all <- read_csv("../../data/lit_review.csv")
spec(data.all)
# Make column headers lowercase
colnames(data.all) <- tolower(colnames(data.all))
# Subset some data
data.fish <- filter(data.all, species_type == "Fish")

data.all <- data.all %>% mutate(movement = 
                                  circatidal_migration |
                                  pynocline_migration |
                                  halocline_migration |
                                  ontogentic_vertical_migration |
                                  vertical_swimming_ability |
                                  horizontal_swimming_ability |
                                  sinking_velocity  | 
                                  diel_vertical_migration) %>% mutate(sensory_ability = ifelse(buffer_size > 0, TRUE, FALSE)) %>% replace_na(list(sensory_ability = FALSE))
```

Summary of all the data
```{r}
#get a summary of all the data
summary(data.all)
```

# Methods

Number of papers and journals
```{r}
length(unique(data.all$title))
length(unique(data.all$journal))
```

# Current trends in biophysical modelling

Figure 1: Publication years
```{r}
data.all$published <- as.factor(data.all$published)
years.data <- data.all %>% select(paper_id, published) %>% distinct(paper_id, published)
years.plot <- ggplot(years.data,aes(published)) + geom_bar() + labs(x="Year published", y="Number of studies") + theme_few() + scale_colour_few()
years.plot
ggsave("../../figs/years.png", plot=years.plot, width=162, height=140, units="mm", dpi=96)
```

Figure 2: The taxa modelled
```{r}
data.all$species_type <- as.factor(data.all$species_type)
taxa.plot <- ggplot(data=data.all,aes(sort_factor(species_type))) + 
  geom_bar() + coord_flip() + ylab("Number of models") + xlab("Modelled taxa") + scale_x_discrete(labels = c("Cnidarian","Gastropod","Macroalgae","Echinoderm","Polychaete","Coral","Crustacean","Mollusc","Bivalvia","Fish","Generic")) +
  theme_few() + scale_colour_few()
ggsave("../../figs/taxa.png", plot=taxa.plot, width=162, height=120, units="mm", dpi=96)
taxa.plot
```

## Model context
```{r}
get_factor_proportion(data.all$species_type)
data.models <- distinct(select(data.all,title, model_reuse, model_name, motivation, geographical_zone))
data.models$model_name <- addNA(data.models$model_name)
data.models$model_reuse <- addNA(data.models$model_reuse)
get_factor_proportion(data.models$model_reuse)
get_factor_proportion(data.models$model_name)
get_factor_proportion(data.models$motivation)
get_factor_proportion(data.models$geographical_zone)
get_factor_proportion(data.all$years_total)
summary(data.all$years_total)
summary(data.all$date_start)
summary(data.all$date_end)
```

## How connectivity studies are parametising the physical model
```{r}
data.models <- distinct(select(data.all,title, physical_model, nested_submodels,model_resolution_min, model_integration, model_time_step))
data.models$physical_model <- addNA(data.models$physical_model)
data.models$nested_submodels <- addNA(data.models$nested_submodels)
data.models$model_integration <- addNA(data.models$model_integration)
get_factor_proportion(data.models$physical_model)
get_factor_proportion(data.models$nested_submodels)
summary(data.models$model_resolution_min)
get_factor_proportion(data.models$model_integration)
summary(data.models$model_time_step)
data.models$model_time_step <- addNA(data.models$model_time_step)
get_factor_proportion(data.models$model_time_step)
```


Table 2: Percentage of biological traits implemented.

PLD
```{r}
data.all$pld_type <- as.factor(data.all$pld_type)
pld_percentage <- length(which(!is.na(data.all$pld_type))) / length(data.all$pld_type) * 100
pld_percentage
```

Settlement competency
```{r}
data.all$settlement_competency_type <- as.factor(data.all$settlement_competency_type)
settlement_percentage <- length(which(!is.na(data.all$settlement_competency_type))) / length(data.all$settlement_competency_type) * 100
settlement_percentage
```

Spawning strategy
```{r}
data.all$run_mode <- as.factor(data.all$run_mode)
spawning.percentage <- length(which(data.all$run_mode == 'Forecast')) / length(data.all$run_mode) * 100
spawning.percentage
```

Mortality
```{r}
mortality.percentage <- length(which((data.all$mortality))) / length(data.all$mortality) * 100
mortality.percentage
```

Growth
```{r}
growth.percentage <- length(which((data.all$growth))) / length(data.all$growth) * 100
growth.percentage
```

Sensory ability
```{r}
#senses <- filter(data.all, buffer_size > 0 | sensory_zone > 0)
sensory_ability.percentage <- length(which(data.all$buffer_size > 0 | data.all$sensory_zone > 0)) / length(data.all$buffer_size) * 100
sensory_ability.percentage
```

Orientation
```{r}
orientation.percentage <- length(which((data.all$directed_swimming))) / length(data.all$directed_swimming) * 100
orientation.percentage
```

Swimming behaviours
```{r}
movement.percentage <- length(which((data.all$movement))) / length(data.all$movement) * 100
movement.percentage
```

### Pelagic larval duration

Fixed pld
```{r}
pld.fixed.percentage <- length(which((data.all$pld_type == 'Fixed'))) / length(data.all$pld_type) * 100
pld.fixed.percentage
```

Variable pld
```{r}
pld.fixed.percentage <- length(which((data.all$pld_type == 'Variable'))) / length(data.all$pld_type) * 100
pld.fixed.percentage
```

Both pld
```{r}
pld.fixed.percentage <- length(which((data.all$pld_type == 'Both'))) / length(data.all$pld_type) * 100
pld.fixed.percentage
```

Range
```{r}
summary(data.all$pld_fixed)
```

### Spawning strategies

```{r}
get_factor_proportion(addNA(data.all$spawning_depth_type))
#get_factor_proportion(addNA(data.all$spawning_initiation))
data.all <- mutate(data.all, spawning_diff = (spawning_settlement_sites - spawning_release_sites) == 0)
get_factor_proportion(addNA(data.all$spawning_diff))
summary(data.all$particles_spawned_at_individual_site)
summary(data.all$particles_spawned_total)
get_factor_proportion(addNA(data.all$particles_spawned_super_individual))
```

#### Mortality & Growth

```{r}
get_factor_proportion(data.all$mortality_function)
summary(filter(data.all,mortality_function == 'Linear')$mortality_rate)
```


#### Movement behaviours

Figure 3: Percentage of models over time (fish and inverts)
```{r}
data.all$published <- as.factor(data.all$published)
papers.comparisons <- data.all %>% gather(behaviours, implemented,passive_movement,movement,directed_swimming, sensory_ability)
papers.comparisons <- papers.comparisons %>% select(paper_id,published,behaviours,implemented,species_type) %>% distinct(paper_id,published,behaviours,implemented,species_type) %>% filter(implemented == TRUE) %>% mutate(is_fish = species_type == 'Fish') %>% mutate(is_invert = species_type != 'Fish' & species_type != 'Generic' & species_type != 'Macroalgae') %>%
  mutate(taxa = if_else(is_fish == TRUE & is_invert == FALSE, 'Fish', if_else(is_invert == TRUE, 'Invertebrate', 'NA'))) %>% filter( taxa == 'Fish' | taxa == 'Invertebrate')

comparisons.plot <- ggplot(papers.comparisons, aes(published)) + geom_bar(aes(fill = behaviours)) +labs( x = "Publication year", y = "Number of models") +theme_few()+ theme(legend.title = element_blank(), legend.position = "top",legend.key.size = unit(5,'mm'),axis.text.x=element_text(angle=90)) +  scale_fill_grey(start = 0.3, end = 0.8, na.value="red",breaks=c("passive_movement","movement","sensory_ability","directed_swimming"), labels = c("Passive", "Movement", "Settlement", "Orientation")) + facet_grid(taxa ~ .)+ annotate(geom = "text", x = 7, y = 14, label = c("A","B")) + guides(fill=guide_legend(nrow=2,byrow=TRUE))


papers.comparisons.prop <- papers.comparisons %>%
  group_by(taxa, published, behaviours, taxa) %>%
  summarise (n = n()) %>%
  mutate(freq = n / sum(n))

prop.plot <- ggplot(papers.comparisons.prop, aes(x=published,y=freq, group=behaviours, colour=behaviours, shape=behaviours)) +labs( x = "Publication year", y = "Proportion")+ geom_line() + geom_point(size=2) + theme_few() + theme(legend.title = element_blank(), legend.position = "top",axis.text.x=element_text(angle=90)) +  scale_colour_grey(breaks=c("passive_movement","movement","sensory_ability","directed_swimming"), labels = c("Passive", "Movement", "Settlement", "Orientation")) + facet_grid(taxa ~ .)+ scale_shape(breaks=c("passive_movement","movement","sensory_ability","directed_swimming"),labels = c("Passive", "Movement", "Settlement", "Orientation"))+ annotate(geom = "text", x = 7, y = 0.9, label = c("C","D"))+ guides(colour=guide_legend(nrow=2,byrow=TRUE))

p <- grid.arrange(comparisons.plot,prop.plot,ncol=2)
ggsave("../../figs/comparisons.png",plot=p,width = 169, height=120, units="mm",dpi=300)
#p <- grid.arrange(
#ggsave("figs/invert_prop.png",plot=p)

```

Overall
```{r}
passive.percentage <- length(which((data.all$passive_movement))) / length(data.all$passive_movement) * 100
passive.percentage
```

```{r}
passive.percentage <- length(which((data.fish$passive_movement))) / length(data.fish$passive_movement) * 100
passive.percentage
```

```{r}
data.movement <- filter(data.all,movement)
get_factor_proportion(data.movement$diel_vertical_migration)
get_factor_proportion(data.movement$ontogentic_vertical_migration)
get_factor_proportion(data.movement$horizontal_swimming_ability)
get_factor_proportion(data.movement$vertical_swimming_ability)
get_factor_proportion(data.movement$circatidal_migration)
get_factor_proportion(data.movement$pynocline_migration)
get_factor_proportion(data.movement$halocline_migration)
get_factor_proportion(data.movement$sinking_velocity)
get_factor_proportion(data.movement$egg_buoyancy)
```

```{r}
length(senses$passive_movement) / length(data.all$passive_movement) * 100
get_factor_proportion(addNA(senses$buffer_size))
summary(senses$buffer_size)
summary(senses$sensory_zone)
```

### Metrics used to describe connectivity

```{r}
get_factor_proportion(data.all$dispersal_kernel)

data.dk <- filter(data.all, dispersal_kernel)
get_factor_proportion(addNA(data.dk$mean_distance))
get_factor_proportion(addNA(data.dk$median_distance))
get_factor_proportion(addNA(data.dk$distance_travelled_max))
get_factor_proportion(addNA(data.dk$distance_travelled_upper_quantile))

data.all <- mutate(data.all, connectivity_metrics = connectivity_metrics_realised | connectivity_metrics_potential)
get_factor_proportion(data.all$connectivity_metrics)
data.cm <- filter(data.all, connectivity_metrics)
get_factor_proportion(addNA(data.cm$self_recruitment))
get_factor_proportion(addNA(data.cm$local_retention))
get_factor_proportion(addNA(data.cm$settlement_success))

get_factor_proportion(data.all$graph_theory)
get_factor_proportion(addNA(data.all$centre_of_mass))
get_factor_proportion(addNA(data.all$isotropy))
get_factor_proportion(addNA(data.all$positive_area))
get_factor_proportion(addNA(data.all$proportion_sites_settled))

data.cm <- data.cm %>% mutate(sr_values = self_recruitment_mean > 0 | self_recruitment_max > 0) %>% mutate(lr_values = local_retention_mean > 0 | local_retention_max > 0) %>% mutate(ss_values = settlement_success_mean > 0 | settlement_success_min > 0)
get_factor_proportion(addNA(data.cm$lr_values))
get_factor_proportion(addNA(data.cm$sr_values))
get_factor_proportion(addNA(data.cm$ss_values))

summary(data.cm$self_recruitment_mean)
summary(data.cm$local_retention_mean)
summary(data.cm$settlement_success_mean)
summary(data.cm$distance_travelled_mean)
```


## Influence of modelling decisions on connectivity values

### Model Resolution

```{r}
resolution.data <- data.all %>% select(model_resolution_min,self_recruitment_mean,settlement_success_mean,
                                       local_retention_mean,distance_travelled_mean) %>% filter(model_resolution_min < 20)
resolution.sr_lm <- lm(model_resolution_min ~ self_recruitment_mean, data = resolution.data)
resolution.ss_lm <- lm(model_resolution_min ~ settlement_success_mean, data = resolution.data)
resolution.lr_lm <- lm(model_resolution_min ~ local_retention_mean, data = resolution.data)
resolution.dd_lm <- lm(model_resolution_min ~ distance_travelled_mean, data = resolution.data)
summary(resolution.sr_lm)
summary(resolution.ss_lm)
summary(resolution.lr_lm)
summary(resolution.dd_lm)
resolution1 <- ggplot(resolution.data,aes(model_resolution_min,self_recruitment_mean)) +   
  geom_point() + 
  labs(x="", y="Self-recruitment (%)")+
  theme_few() + 
  scale_colour_few() + 
  scale_y_continuous(limits = c(0, 1.0)) +
  theme(axis.title = element_text(size = 9), axis.text = element_text(size = 8))
resolution2 <- ggplot(resolution.data,aes(model_resolution_min,local_retention_mean)) + 
  geom_point() + 
  labs(x="", y="Local retention (%)") +
  geom_smooth(method = lm,colour='black') + 
  theme_few() + 
  scale_colour_few()+ 
  scale_y_continuous(limits = c(0, 1.0)) +
  theme(axis.title = element_text(size = 9), axis.text = element_text(size = 8))
resolution3 <- ggplot(resolution.data,aes(model_resolution_min,settlement_success_mean)) + 
  geom_point()+ 
  labs(x="", y="Settlement success (%)") +
  theme_few() + 
  scale_colour_few() + 
  scale_y_continuous(limits = c(0, 1.0)) +
  theme(axis.title = element_text(size = 9), axis.text = element_text(size = 8))
resolution4 <- ggplot(resolution.data,aes(model_resolution_min,distance_travelled_mean)) + 
  geom_point() + 
  labs(x="Model resolution (km^2)", y="Dispersal distance (km)") +
  theme_few() + 
  scale_colour_few() + 
  theme(axis.title = element_text(size = 9), axis.text = element_text(size = 8))
grid.arrange(resolution1,resolution2,resolution3,resolution4)
```

### Biological parameterisation


PLD

```{r}
data.pld <- filter(data.all, pld_fixed < 150)
pld.sr_lm <- lm(self_recruitment_mean ~ pld_fixed, data = data.pld)
pld.ss_lm <-
lm(settlement_success_mean ~ pld_fixed, data = data.pld)
pld.lr_lm <- lm(local_retention_mean ~ pld_fixed, data = data.pld)
pld.dd_lm <-
lm(distance_travelled_mean ~ pld_fixed, data = data.pld)
summary(pld.sr_lm)
summary(pld.lr_lm)
summary(pld.ss_lm)
summary(pld.dd_lm)
pld1 <- ggplot(data.pld, aes(pld_fixed, self_recruitment_mean)) +
  geom_point() + 
  labs(x = "", y = "") +
  theme_few() + 
  scale_colour_few() + 
  scale_y_continuous(limits = c(0, 1.0)) +
  theme(axis.text=element_text(size=8))
pld2 <- ggplot(data.pld, aes(pld_fixed, local_retention_mean)) + 
  geom_point() + 
  labs(x ="", y = "") +
  geom_smooth(method = lm,colour='black') + 
  theme_few() + 
  scale_colour_few() + 
  scale_y_continuous(limits = c(0, 1.0)) +
  theme(axis.text=element_text(size=8))
pld3 <- ggplot(data.pld, aes(pld_fixed, settlement_success_mean)) + 
  geom_point() + 
  labs(x ="", y = "") +
  theme_few() + 
  scale_colour_few() + 
  scale_y_continuous(limits = c(0, 1.0)) +
  theme(axis.text=element_text(size=8))
pld4 <- ggplot(data.pld, aes(pld_fixed, distance_travelled_mean)) + 
  geom_point() + 
  labs(x ="PLD (days)", y = "") +
  theme_few() + 
  scale_colour_few() +
  theme(axis.title = element_text(size = 9), axis.text = element_text(size = 8))
grid.arrange(pld1, pld2, pld3, pld4)
```


### Settlement competency window
```{r}
data.sr <- data.all %>% mutate(window=pld_fixed-settlement_competency_type_start) %>% filter(window < 50)
window.sr_lm <- lm(window ~ self_recruitment_mean, data = data.sr)
window.ss_lm <- lm(window ~ settlement_success_mean, data = data.sr)
window.lr_lm <- lm(window ~ local_retention_mean, data = data.sr)
window.dd_lm <- lm(window ~ distance_travelled_mean, data = data.sr)
summary(window.sr_lm)
summary(window.ss_lm)
summary(window.lr_lm)
summary(window.dd_lm)
window1 <- ggplot(data.sr,aes(window,self_recruitment_mean)) + 
  geom_point() + 
  geom_smooth(method=lm,colour='black') + 
  labs(x="", y="")+
  theme_few() + 
  scale_colour_few() + 
  scale_y_continuous(limits = c(0, 1.0))+
  theme(axis.text=element_text(size=8))

window2 <- ggplot(data.sr,aes(window,local_retention_mean)) + 
  geom_point() + 
  geom_smooth(method=lm,colour='black',linetype = "dashed")+ 
  labs(x="", y="")+
  theme_few() + 
  scale_colour_few() + 
  scale_y_continuous(limits = c(0, 1.0))+
  theme(axis.text=element_text(size=8))

window3 <- ggplot(data.sr,aes(window,settlement_success_mean)) + 
  geom_point() + 
  labs(x="", y="")+ 
  theme_few()+
  scale_colour_few() + 
  scale_y_continuous(limits = c(0, 1.0)) +
  theme(axis.text=element_text(size=8))

window4 <- ggplot(data.sr,aes(window,distance_travelled_mean)) + 
  geom_point() + 
  labs(x="Settlement window (days)", y="")+
  theme_few() + 
  scale_colour_few() + 
  theme(axis.title=element_text(size=9),axis.text=element_text(size=8))

p <- grid.arrange(resolution1, pld1, window1,
                  resolution2, pld2, window2,
                  resolution3, pld3, window3,
                  resolution4, pld4, window4,
                  ncol = 3)
ggsave("../../figs/metrics_panel.png",plot=p,width = 169, height=150, units="mm",dpi=96)
```


#### Mortality

Figure for mortality comparisons with metrics
```{r}
mortality.prop <- data.all %>% filter(mortality == TRUE) %>% group_by(mortality_function) %>% summarise (n = n()) %>% mutate(freq = n / sum(n))
mort1 <- ggplot(data.all, aes(mortality, self_recruitment_mean)) + geom_boxplot() + #geom_jitter(width = 0.1)+ 
  labs(x="", y="Self-recruitment")+ theme_few() + scale_fill_grey() +
  scale_y_continuous(limits = c(0, 1.0)) + scale_x_discrete(labels=c("None","Included"))
mort2 <- ggplot(data.all, aes(mortality, local_retention_mean)) + geom_boxplot()+ #geom_jitter(width = 0.1) +
  labs(x="", y="Local retention")+ theme_few() + scale_fill_few() +
  scale_y_continuous(limits = c(0, 1.0))+ scale_x_discrete(labels=c("None","Included"))
mort3 <- ggplot(data.all, aes(mortality, settlement_success_mean)) + geom_boxplot()+ #geom_jitter(width = 0.1) +
  labs(x="Mortality", y="Settlement success")+ theme_few() + scale_fill_few() +
  scale_y_continuous(limits = c(0, 1.0))+ scale_x_discrete(labels=c("None","Included"))
mort4 <- ggplot(data.all, aes(mortality, distance_travelled_mean)) + geom_boxplot()+ #geom_jitter(width = 0.1) +
  labs(x="Mortality", y="Dispersal distance (km)")+ theme_few() + scale_fill_few()+ scale_x_discrete(labels=c("None","Included"))
p <- grid.arrange(mort1,mort2,mort3,mort4)
ggsave("../../figs/mortality.png",plot=p,width = 169, height=120, units="mm",dpi=96)


bartlett.test(self_recruitment_mean ~ mortality, data=data.all)
bartlett.test(local_retention_mean ~ mortality, data=data.all)
bartlett.test(settlement_success_mean ~ mortality, data=data.all)
bartlett.test(distance_travelled_mean ~ mortality, data=data.all)
t.test(self_recruitment_mean ~ mortality, data=data.all, var.equal=TRUE)
t.test(local_retention_mean ~ mortality, data=data.all, var.equal=FALSE)
t.test(settlement_success_mean ~ mortality, data=data.all, var.equal=TRUE)
t.test(distance_travelled_mean ~ mortality, data=data.all, var.equal=FALSE)
```

#### Movement behaviours

Figure for the movement behaviours with metrics

```{r}
behaviour.data <- data.all %>% mutate(settlement = sensory_ability & passive_movement & !directed_swimming) %>% 
  mutate(orien_settle = directed_swimming & sensory_ability) %>% 
  mutate(move_settle = sensory_ability & movement & !directed_swimming) %>% 
  mutate(no_behav = passive_movement == TRUE & sensory_ability == FALSE & directed_swimming == FALSE) %>% 
  mutate(orien = directed_swimming == TRUE & sensory_ability == FALSE & passive_movement == FALSE) %>% 
  mutate(move = passive_movement == FALSE & sensory_ability == FALSE & directed_swimming == FALSE)

behaviour.data <- behaviour.data %>% 
  gather(behaviours, implemented,no_behav,move,orien,settlement,orien_settle,move_settle) %>% 
  filter(implemented == TRUE)
behaviour.data$behaviours <- factor(behaviour.data$behaviours,levels = c('no_behav','move','settlement','move_settle','orien','orien_settle'),ordered=TRUE)


behaviour1 <- ggplot(behaviour.data,aes(behaviours,self_recruitment_mean)) + 
  geom_boxplot(na.rm = TRUE) + 
  #geom_jitter(width=0.1) + 
  scale_x_discrete(limits=c('no_behav','move','settlement','move_settle','orien','orien_settle'), labels=c("P","M","S","MS","O","OS")) + 
  theme_few() + 
  scale_fill_few() +
  labs(x="", y="Self-recruitment") +
  scale_y_continuous(limits = c(0, 1.0))

behaviour2 <- ggplot(behaviour.data,aes(behaviours,local_retention_mean)) + 
  geom_boxplot(na.rm = TRUE) + 
  #geom_jitter(width=0.1) +
  scale_x_discrete(limits=c('no_behav','move','settlement','move_settle','orien','orien_settle'),labels=c("P","M","S","MS","O","OS")) + 
  theme_few() + 
  scale_fill_few() +
  labs(x="", y="Local retention") +
  scale_y_continuous(limits = c(0, 1.0))

behaviour3 <- ggplot(behaviour.data,aes(behaviours,settlement_success_mean)) + 
  geom_boxplot(na.rm = TRUE) + 
  #geom_jitter(width=0.1) +
  scale_x_discrete(limits=c('no_behav','move','settlement','move_settle','orien','orien_settle'), labels=c("P","M","S","MS","O","OS")) + 
  theme_few() + 
  scale_fill_few()+
  labs(x="Behaviour", y="Settlement success") +
  scale_y_continuous(limits = c(0, 1.0))

behaviour4 <- ggplot(behaviour.data,aes(behaviours,distance_travelled_mean)) + 
  geom_boxplot(na.rm = TRUE) + 
  #geom_jitter(width=0.1) +
  scale_x_discrete(limits=c('no_behav','move','settlement','move_settle','orien','orien_settle'), labels=c("P","M","S","MS","O","OS")) + 
  theme_few() + 
  scale_fill_few() +
  labs(x="Behaviour", y="Dispersal distance (km)")


p <- grid.arrange(behaviour1,behaviour2,behaviour3,behaviour4)
ggsave("../../figs/behaviours.png",plot=p,width = 169, height=120, units="mm",dpi=96)
```

Statistics for behaviour

Self-recruitment
```{r}
behaviour.data <- mutate(behaviour.data, sr_t = self_recruitment_mean + 1)
qqp(behaviour.data$self_recruitment_mean,"lnorm")
glm.sr <- glm(sr_t ~ behaviours, family=gaussian(link="log"), data=behaviour.data)
lsmeans.sr <- lsmeans(glm.sr, ~ behaviours)
summary(pairs(lsmeans(glm.sr, ~ behaviours)), type = "response")
cld(lsmeans.sr,alpha = 0.05, Letters = letters, adjust="tukey")
```

Local retention
```{r}
qqp(behaviour.data$local_retention_mean,"norm")
lm.lr <- lm(local_retention_mean ~ behaviours, data=behaviour.data)
lsmeans.lm <- lsmeans(lm.lr, ~ behaviours)
summary(pairs(lsmeans(lm.lr, ~ behaviours)), type = "response")
cld(lsmeans.lm,alpha = 0.05, Letters = letters, adjust="tukey")
```

Settlement success

```{r}
behaviour.data <- mutate(behaviour.data, ss_t = settlement_success_mean + 1)
qqp(behaviour.data$settlement_success_mean,"lnorm")
glm.ss <- glm(ss_t ~ behaviours, family=gaussian(link="log"), data=behaviour.data)
lsmeans.ss <- lsmeans(glm.ss, ~ behaviours)
summary(pairs(lsmeans(glm.ss, ~ behaviours)), type = "response")
cld(lsmeans.ss,alpha = 0.05, Letters = letters, adjust="tukey")
```



Dispersal distance
```{r}
# Dispersal distance
qqp(behaviour.data$distance_travelled_mean,"lnorm")
glm.dist <- glm(distance_travelled_mean ~ behaviours, family=gaussian(link="log"), data=behaviour.data)
lsmeans.dist <- lsmeans(glm.dist, ~ behaviours)
summary(pairs(lsmeans(glm.dist, ~ behaviours)), type = "response")
cld(lsmeans.dist,alpha = 0.05, Letters = letters, adjust="tukey")
```


