---
title: "Graph theory analysis for my theoreticla chapter"
output: html_notebook
---

Packages required
```{r, include=FALSE}
library(igraph)
library(NetIndices)
```


Load the data
```{r,include=FALSE}
load(file="phase1.rda")
load(file="phase2.rda")
load(file="phase3.rda")
load(file="reefs.rda")
```

Passive graph analysis
```{r}
rownames(passive.conn.regions) <- passive.regions$settle.region[-18:-19]
graph.passive <- graph_from_adjacency_matrix(passive.conn.regions[,-18:-19], mode= c("directed"), weighted = TRUE)
plot(graph.passive, layout=layout.fruchterman.reingold)

as <- authority_score(graph.passive)$vector
plot(graph.passive, vertex.size = as*30, main="Authorities")

graph.passive.adj <- get.adjacency(graph.passive, sparse = FALSE)
graph.passive.ind <- GenInd(graph.passive.adj)
graph.passive.ind$C

connectance.data <- tribble(~scenario, ~model, ~connectance,
                            "behaviour", "passive", graph.passive.ind$C)
```


Passive-surface graph analysis
```{r}
rownames(passive.surface.conn.regions) <- passive.surface.regions$settle.region[-18:-20]
graph.passive.surface <- graph_from_adjacency_matrix(passive.surface.conn.regions[,-18:-20], mode= c("directed"), weighted = TRUE)
plot(graph.passive.surface, layout=layout.fruchterman.reingold)

as <- authority_score(graph.passive.surface)$vector
plot(graph.passive.surface, vertex.size = as*30, main="Authorities")

graph.passive.surface.adj <- get.adjacency(graph.passive.surface, sparse = FALSE)
graph.passive.surface.ind <- GenInd(graph.passive.surface.adj)
graph.passive.surface.ind$C

connectance.data <- add_row(connectance.data, scenario = "behaviour", model = "passive+va", connectance = graph.passive.surface.ind$C)
```


diel graph analysis
```{r}
rownames(diel.conn.regions) <- diel.regions$settle.region[-18:-19]
graph.diel <- graph_from_adjacency_matrix(diel.conn.regions[,-18:-19], mode= c("directed"), weighted = TRUE)
plot(graph.diel, layout=layout.fruchterman.reingold)

as <- authority_score(graph.diel)$vector
plot(graph.diel, vertex.size = as*30, main="Authorities")

graph.diel.adj <- get.adjacency(graph.diel, sparse = FALSE)
graph.diel.ind <- GenInd(graph.diel.adj)
graph.diel.ind$C
connectance.data <- add_row(connectance.data, scenario = "behaviour", model = "dvm", connectance = graph.diel.ind$C)
```
ovm graph analysis
```{r}
rownames(ovm.conn.regions) <- ovm.regions$settle.region[-18:-19]
graph.ovm <- graph_from_adjacency_matrix(ovm.conn.regions[,-18:-19], mode= c("directed"), weighted = TRUE)
plot(graph.ovm, layout=layout.fruchterman.reingold)

as <- authority_score(graph.ovm)$vector
plot(graph.ovm, vertex.size = as*30, main="Authorities")

graph.ovm.adj <- get.adjacency(graph.ovm, sparse = FALSE)
graph.ovm.ind <- GenInd(graph.ovm.adj)
graph.ovm.ind$C
connectance.data <- add_row(connectance.data, scenario = "behaviour", model = "ovm", connectance = graph.ovm.ind$C)
```

orientate graph analysis
```{r}
orientate.regions <- orientate.regions[-18,]
rownames(orientate.conn.regions) <- orientate.regions$settle.region[-18:-19]
graph.orientate <- graph_from_adjacency_matrix(orientate.conn.regions[,-18:-19], mode= c("directed"), weighted = TRUE)
plot(graph.orientate, layout=layout.fruchterman.reingold)

as <- authority_score(graph.orientate)$vector
plot(graph.orientate, vertex.size = as*30, main="Authorities")

graph.orientate.adj <- get.adjacency(graph.orientate, sparse = FALSE)
graph.orientate.ind <- GenInd(graph.orientate.adj)
graph.orientate.ind$C
connectance.data <- add_row(connectance.data, scenario = "behaviour", model = "ohs", connectance = graph.orientate.ind$C)
```



ovm.orientate graph analysis
```{r}
ovm.orientate.regions <- ovm.orientate.regions[-18,]
rownames(ovm.orientate.conn.regions) <- ovm.orientate.regions$settle.region[-18:-19]
graph.ovm.orientate <- graph_from_adjacency_matrix(ovm.orientate.conn.regions[,-18:-19], mode= c("directed"), weighted = TRUE)
plot(graph.ovm.orientate, layout=layout.fruchterman.reingold)

as <- authority_score(graph.ovm.orientate)$vector
plot(graph.ovm.orientate, vertex.size = as*30, main="Authorities")

graph.ovm.orientate.adj <- get.adjacency(graph.ovm.orientate, sparse = FALSE)
graph.ovm.orientate.ind <- GenInd(graph.ovm.orientate.adj)
graph.ovm.orientate.ind$C
connectance.data <- add_row(connectance.data, scenario = "behaviour", model = "ovm+ohs", connectance = graph.ovm.orientate.ind$C)
```

orientate-surface graph analysis
```{r}
orientate.surface.regions <- orientate.surface.regions[-18,]
rownames(orientate.surface.conn.regions) <- orientate.surface.regions$settle.region[-18:-19]
graph.orientate.surface <- graph_from_adjacency_matrix(orientate.surface.conn.regions[,-18:-19], mode= c("directed"), weighted = TRUE)
plot(graph.orientate.surface, layout=layout.fruchterman.reingold)

as <- authority_score(graph.orientate.surface)$vector
plot(graph.orientate.surface, vertex.size = as*30, main="Authorities")

graph.orientate.surface.adj <- get.adjacency(graph.orientate, sparse = FALSE)
graph.orientate.surface.ind <- GenInd(graph.orientate.surface.adj)
graph.orientate.surface.ind$C
connectance.data <- add_row(connectance.data, scenario = "behaviour", model = "ohs+va", connectance = graph.orientate.surface.ind$C)
```

diel.orientate graph analysis
```{r}
diel.orientate.regions <- diel.orientate.regions[-18,]
rownames(diel.orientate.conn.regions) <- diel.orientate.regions$settle.region[-18:-19]
graph.diel.orientate <- graph_from_adjacency_matrix(diel.orientate.conn.regions[,-18:-19], mode= c("directed"), weighted = TRUE)
plot(graph.diel.orientate, layout=layout.fruchterman.reingold)

as <- authority_score(graph.diel.orientate)$vector
plot(graph.diel.orientate, vertex.size = as*30, main="Authorities")

graph.diel.orientate.adj <- get.adjacency(graph.diel.orientate, sparse = FALSE)
graph.diel.orientate.ind <- GenInd(graph.diel.orientate.adj)
graph.diel.orientate.ind$C
connectance.data <- add_row(connectance.data, scenario = "behaviour", model = "dvm+ohs", connectance = graph.diel.orientate.ind$C)
```

diel.ovm.orientate graph analysis
```{r}
diel.ovm.orientate.regions <- diel.ovm.orientate.regions[-18,]
rownames(diel.ovm.orientate.conn.regions) <- diel.ovm.orientate.regions$settle.region[-18:-19]
graph.diel.ovm.orientate <- graph_from_adjacency_matrix(diel.ovm.orientate.conn.regions[,-18:-19], mode= c("directed"), weighted = TRUE)
plot(graph.diel.ovm.orientate, layout=layout.fruchterman.reingold)

as <- authority_score(graph.diel.ovm.orientate)$vector
plot(graph.diel.ovm.orientate, vertex.size = as*30, main="Authorities")

graph.diel.ovm.orientate.adj <- get.adjacency(graph.diel.ovm.orientate, sparse = FALSE)
graph.diel.ovm.orientate.ind <- GenInd(graph.diel.ovm.orientate.adj)
graph.diel.ovm.orientate.ind$C
connectance.data <- add_row(connectance.data, scenario = "behaviour", model = "dvm+ovm+ohs", connectance = graph.diel.ovm.orientate.ind$C)
```

diel.ovm graph analysis
```{r}
diel.ovm.regions <- diel.ovm.regions[-18,]
rownames(diel.ovm.conn.regions) <- diel.ovm.regions$settle.region[-18:-19]
graph.diel.ovm <- graph_from_adjacency_matrix(diel.ovm.conn.regions[,-18:-19], mode= c("directed"), weighted = TRUE)
plot(graph.diel.ovm, layout=layout.fruchterman.reingold)

as <- authority_score(graph.diel.ovm)$vector
plot(graph.diel.ovm, vertex.size = as*30, main="Authorities")

graph.diel.ovm.adj <- get.adjacency(graph.diel.ovm, sparse = FALSE)
graph.diel.ovm.ind <- GenInd(graph.diel.ovm.adj)
graph.diel.ovm.ind$C
connectance.data <- add_row(connectance.data, scenario = "behaviour", model = "dvm+ovm", connectance = graph.diel.ovm.ind$C)
```

ovm.labrid graph analysis
```{r}
ovm.labrid.regions <- ovm.labrid.regions[-18,]
rownames(ovm.labrid.conn.regions) <- ovm.labrid.regions$settle.region[-18:-19]
graph.ovm.labrid <- graph_from_adjacency_matrix(ovm.labrid.conn.regions[,-18:-19], mode= c("directed"), weighted = TRUE)
plot(graph.ovm.labrid, layout=layout.fruchterman.reingold)

as <- authority_score(graph.ovm.labrid)$vector
plot(graph.ovm.labrid, vertex.size = as*30, main="Authorities")

graph.ovm.labrid.adj <- get.adjacency(graph.ovm.labrid, sparse = FALSE)
graph.ovm.labrid.ind <- GenInd(graph.ovm.labrid.adj)
graph.ovm.labrid.ind$C
connectance.data <- add_row(connectance.data, scenario = "ovm-strategy", model = "strategy-1", connectance = graph.ovm.labrid.ind$C)
```

ovm.mullid graph analysis
```{r}
ovm.mullid.regions <- ovm.mullid.regions[-18,]
rownames(ovm.mullid.conn.regions) <- ovm.mullid.regions$settle.region[-18:-19]
graph.ovm.mullid <- graph_from_adjacency_matrix(ovm.mullid.conn.regions[,-18:-20], mode= c("directed"), weighted = TRUE)
plot(graph.ovm.mullid, layout=layout.fruchterman.reingold)

as <- authority_score(graph.ovm.mullid)$vector
plot(graph.ovm.mullid, vertex.size = as*30, main="Authorities")

graph.ovm.mullid.adj <- get.adjacency(graph.ovm.mullid, sparse = FALSE)
graph.ovm.mullid.ind <- GenInd(graph.ovm.mullid.adj)
graph.ovm.mullid.ind$C
connectance.data <- add_row(connectance.data, scenario = "ovm-strategy", model = "strategy-2", connectance = graph.ovm.mullid.ind$C)
connectance.data <- add_row(connectance.data, scenario = "ovm-strategy", model = "strategy-3", connectance = graph.ovm.ind$C)
```


ovm.scarid graph analysis
```{r}
ovm.scarid.regions <- ovm.scarid.regions[-18,]
rownames(ovm.scarid.conn.regions) <- ovm.scarid.regions$settle.region[-18:-19]
graph.ovm.scarid <- graph_from_adjacency_matrix(ovm.scarid.conn.regions[,-18:-19], mode= c("directed"), weighted = TRUE)
plot(graph.ovm.scarid, layout=layout.fruchterman.reingold)

as <- authority_score(graph.ovm.scarid)$vector
plot(graph.ovm.scarid, vertex.size = as*30, main="Authorities")

graph.ovm.scarid.adj <- get.adjacency(graph.ovm.scarid, sparse = FALSE)
graph.ovm.scarid.ind <- GenInd(graph.ovm.scarid.adj)
graph.ovm.scarid.ind$C
connectance.data <- add_row(connectance.data, scenario = "ovm-strategy", model = "strategy-4", connectance = graph.ovm.scarid.ind$C)
```

ovm.serranid graph analysis
```{r}
ovm.serranid.regions <- ovm.serranid.regions[-18,]
rownames(ovm.serranid.conn.regions) <- ovm.serranid.regions$settle.region[-18:-19]
graph.ovm.serranid <- graph_from_adjacency_matrix(ovm.serranid.conn.regions[,-18:-19], mode= c("directed"), weighted = TRUE)
plot(graph.ovm.serranid, layout=layout.fruchterman.reingold)

as <- authority_score(graph.ovm.serranid)$vector
plot(graph.ovm.serranid, vertex.size = as*30, main="Authorities")

graph.ovm.serranid.adj <- get.adjacency(graph.ovm.serranid, sparse = FALSE)
graph.ovm.serranid.ind <- GenInd(graph.ovm.serranid.adj)
graph.ovm.serranid.ind$C
connectance.data <- add_row(connectance.data, scenario = "ovm-strategy", model = "strategy-5", connectance = graph.ovm.serranid.ind$C)
```

ovm.scorpaenid graph analysis
```{r}
ovm.scorpaenid.regions <- ovm.scorpaenid.regions[-18,]
rownames(ovm.scorpaenid.conn.regions) <- ovm.scorpaenid.regions$settle.region[-18:-19]
graph.ovm.scorpaenid <- graph_from_adjacency_matrix(ovm.scorpaenid.conn.regions[,-18:-19], mode= c("directed"), weighted = TRUE)
plot(graph.ovm.scorpaenid, layout=layout.fruchterman.reingold)

as <- authority_score(graph.ovm.scorpaenid)$vector
plot(graph.ovm.scorpaenid, vertex.size = as*30, main="Authorities")

graph.ovm.scorpaenid.adj <- get.adjacency(graph.ovm.scorpaenid, sparse = FALSE)
graph.ovm.scorpaenid.ind <- GenInd(graph.ovm.scorpaenid.adj)
graph.ovm.scorpaenid.ind$C
connectance.data <- add_row(connectance.data, scenario = "ovm-strategy", model = "strategy-6", connectance = graph.ovm.scorpaenid.ind$C)
```

ovm.synodontid graph analysis
```{r}
ovm.synodontid.regions <- ovm.synodontid.regions[-18,]
rownames(ovm.synodontid.conn.regions) <- ovm.synodontid.regions$settle.region[-18:-19]
graph.ovm.synodontid <- graph_from_adjacency_matrix(ovm.synodontid.conn.regions[,-18:-19], mode= c("directed"), weighted = TRUE)
plot(graph.ovm.synodontid, layout=layout.fruchterman.reingold)

as <- authority_score(graph.ovm.synodontid)$vector
plot(graph.ovm.synodontid, vertex.size = as*30, main="Authorities")

graph.ovm.synodontid.adj <- get.adjacency(graph.ovm.synodontid, sparse = FALSE)
graph.ovm.synodontid.ind <- GenInd(graph.ovm.synodontid.adj)
graph.ovm.synodontid.ind$C
connectance.data <- add_row(connectance.data, scenario = "ovm-strategy", model = "strategy-7", connectance = graph.ovm.synodontid.ind$C)
```

ovm.timestep graph analysis
```{r}
ovm.timestep.regions <- ovm.timestep.regions[-18,]
rownames(ovm.timestep.conn.regions) <- ovm.timestep.regions$settle.region[-18:-19]
graph.ovm.timestep <- graph_from_adjacency_matrix(ovm.timestep.conn.regions[,-18:-19], mode= c("directed"), weighted = TRUE)
plot(graph.ovm.timestep, layout=layout.fruchterman.reingold)

as <- authority_score(graph.ovm.timestep)$vector
plot(graph.ovm.timestep, vertex.size = as*30, main="Authorities")

graph.ovm.timestep.adj <- get.adjacency(graph.ovm.timestep, sparse = FALSE)
graph.ovm.timestep.ind <- GenInd(graph.ovm.timestep.adj)
graph.ovm.timestep.ind$C
connectance.data <- add_row(connectance.data, scenario = "ovm-method", model = "timestep", connectance = graph.ovm.timestep.ind$C)
```

ovm.daily graph analysis
```{r}
ovm.daily.regions <- ovm.daily.regions[-18,]
rownames(ovm.daily.conn.regions) <- ovm.daily.regions$settle.region[-18:-19]
graph.ovm.daily <- graph_from_adjacency_matrix(ovm.daily.conn.regions[,-18:-19], mode= c("directed"), weighted = TRUE)
plot(graph.ovm.daily, layout=layout.fruchterman.reingold)

as <- authority_score(graph.ovm.daily)$vector
plot(graph.ovm.daily, vertex.size = as*30, main="Authorities")

graph.ovm.daily.adj <- get.adjacency(graph.ovm.daily, sparse = FALSE)
graph.ovm.daily.ind <- GenInd(graph.ovm.daily.adj)
graph.ovm.daily.ind$C
connectance.data <- add_row(connectance.data, scenario = "ovm-method", model = "daily", connectance = graph.ovm.daily.ind$C)
connectance.data <- add_row(connectance.data, scenario = "ovm-method", model = "stage", connectance = graph.ovm.ind$C)
```

```{r}
save(connectance.data,file="graph.rda")
```

